---
title: "Beyoko"
author: "Grace Beyoko"
format: html
---

```{r, warning=FALSE, message=FALSE}
here::i_am("galatic_empire.Rproj")
library(here)
library(vroom)
library(stringr)
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
```

## Question 2

[Here](https://github.com/GraceBeyoko/galatic_empire.git) is the link to my github repository.

## Question 3

```{r}
planet <- vroom(here("data","Data_planets.csv"),
                locale = locale(decimal_mark = ","),
                na= "xx")
```



```{r}
## Question 4

```{r}
nb_observation <- 
  nrow(planet)

nb_variable <-
  ncol(planet)

na_key <-
  planet |>
  filter(is.na(planet_key)) |> nrow()
            
na_planet <-
  planet |>
  filter(is.na(PLANET)) |> nrow()

na_star_idx <- planet |> 
  filter(is.na(Star_idx)) |> nrow()

na_mass <- 
  planet |> 
  filter(is.na(Mass)) |> nrow() 

na_density <- planet |>
  filter(is.na(Density)) |> nrow()

na_radius <- planet |> 
  filter(is.na(`Relative Radius`)) |> nrow()
  
na_terrain <- planet |> 
  filter(is.na(type_terrain)) |> nrow()

na_climate <- planet |> 
  filter(is.na(`type of climate`)) |> nrow()

na_obs <- 
   planet |>
   mutate(across(everything(), is.na)) |>
   rowwise() |>
   summarise(na_var = any(c_across(everything()))) |>
   summarise(sum(na_var))
```

| nb_obsv            | nb_var          | na_key     | na_mass     | na_planet     | na_radius     | na_star_idx     | na_terrain     | na_climate     | na_density     | number of row with NA |
|-------|-------|-------|-------|-------|-------|-------|-------|-------|-------|-------|
| `r nb_observation` | `r nb_variable` | `r na_key` | `r na_mass` | `r na_planet` | `r na_radius` | `r na_star_idx` | `r na_terrain` | `r na_climate` | `r na_density` | `r na_obs`            |

## Question 5

```{r}
planet |>
  filter(!is.na(Mass)) |>
  ggplot(aes(x=Density, y=Mass)) + geom_col()
```

## Question 6

```{r}
planet |>
  slice_min(Density) |>
   select(PLANET, Density)

planet |>
  slice_min(Star_idx) |>
   select(PLANET, Star_idx)

planet |>
  slice_min(Mass) |>
   select(PLANET, Mass)

planet |>
  slice_min(`Relative Radius`) |>
   select(PLANET, `Relative Radius`)
```
